Methods for Large Scale Learning to Rank

### 2014-04-14 report/Chapters/BenchmarkResults.tex
LETOR 2.0 results

\subsubsection{Results}

>>>>

\subsubsection{Results}
Table \ref{tab:letor2.0_results} shows the performance of the baseline methods on the datasets in the LETOR 2.0 collection.
\begin{table}
\begin{tabular}{l|lll}
 & OHSUMED & TD2003 & TD2004 \\
 \hline 
RankBoost & 0.4356 & 0.2851 & 0.4716 \\ 
Rank\acs{SVM} & 0.4411 & 0.3410 & 0.4201 \\ 
FRank & 0.4423 & 0.3357 & 0.4708 \\ 
ListNet & 0.4489 & 0.3743 & 0.4579 \\ 
AdaRank-\acs{MAP} & 0.4385 & 0.1940 & 0.4063 \\ 
AdaRank-\acs{nDCG} & 0.4369 & 0.2702 & 0.3878 \\ 
\acs{MHR} & 0.4423 &  &  \\ 
\end{tabular}
\caption{\acs{nDCG}@10 results of baseline methods on LETOR 2.0}
\label{tab:letor2.0_results}
\end{table}
